---
title: 'My Final College Paper'
author: 'Your R. Name'
date: 'May 20xx'
institution: 'Reed College'
division: 'Mathematics and Natural Sciences'
advisor: 'Advisor F. Name'
# If you have more two advisors, un-silence line 7
#altadvisor: 'Your Other Advisor'
department: 'Mathematics'
degree: 'Bachelor of Arts'
knit: bookdown::render_book
site: bookdown::bookdown_site

# The next two lines allow you to change the spacing in your thesis. You can 
# switch out \onehalfspacing with \singlespacing or \doublespacing, if desired.
header-includes:
    - \usepackage{setspace}\onehalfspacing
    - \usepackage{amsmath}
    - \usepackage{amssymb} 

# This will automatically install the {remotes} package and {thesisdown}
# Change this to FALSE if you'd like to install them manually on your own.
params:
  'Install needed packages for {thesisdown}': True
  
# Remove the hashtag to specify which version of output you would like.
# Can only choose one at a time.
output:
   thesisdown::thesis_pdf: default
#  thesisdown::thesis_gitbook: default         
#  thesisdown::thesis_word: default
#  thesisdown::thesis_epub: default

# If you are creating a PDF you'll need to write your preliminary content 
# (e.g., abstract, acknowledgements) below or use code similar to line 25-26 
# for the .RMD files. If you are NOT producing a PDF, delete or silence
# lines 25-39 in this YAML header.
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab 
# is needed on the line after the `|`.
acknowledgements: |
  This thesis was possible due to the support of many people. I would like to express my gratitude to my primary supervisor, Prof. Federico Crudu. His guidance, expertise and belief in my abilities pushed me to do my best. I would also like to thank my secondary supervisor, Prof. Guiliano Curatola for his suggestions and advice. Profs. Arjun Jayadev and Anand Shrivastava of Azim Premji University provided vital feedback through various stages of my work. I would also like to thank the University of Siena for providing academic support and an ideal atmosphere to carry out research. Finally, my research would be incomplete if not for the emotional succour and care from my parents and brother back in India. Their patience and encouragement gave me the motivation needed to cross the finish line, and it is to them that I dedicate this thesis.
# Specify the location of the bibliography below
bibliography: bib/thesis.bib
# Download your specific csl file and refer to it in the line below.
csl: csl/apa.csl
### link highlighting ###
colored-not-bordered-links: true # true = highlight links by coloring text; false = highlight links with a border

# Set the link text/border coloring here, in RGB. 
# Comment out a variable to use whatever the text's existing color is.
# If printing a physical version of your thesis, you'll want to comment out all of these.
urlcolor-rgb: "0,0,139"     # web addresses
citecolor-rgb: "0,33,71"    # citations
linkcolor-rgb: "0,0,139"    # links to sections in your thesis

# Make page number, not text, be link in TOC, LOF, and LOT. Otherwise, section link
# highlighting may look a bit excessive.
toc-link-page-numbers: true
link-citations: yes
linkcolor: blue
always_allow_html: yes
fontsize: 12pt
lot: true
lof: true
---

```{=html}
<!--
Above is the YAML (YAML Ain't Markup Language) header that includes a lot of 
metadata used to produce the document.  Be careful with spacing in this header!

If you'd prefer to not include a Dedication, for example, simply delete the section entirely, or silence them (add # before each line). 

If you have other LaTeX packages you would like to include, delete the # before header-includes and list the packages after hyphens on new lines.

If you'd like to include a comment that won't be produced in your resulting file enclose it in a block like this.

If you receive a duplicate label error after knitting, make sure to delete the index.Rmd file and then knit again.
-->
```
```{r include_packages, include=FALSE}
# This chunk ensures that the thesisdown package is
# installed and loaded. This thesisdown package includes
# the template files for the thesis.
if (!require(remotes)) {
  if (params$`Install needed packages for {thesisdown}`) {
    install.packages("remotes", repos = "https://cran.rstudio.com")
  } else {
    stop(
      paste('You need to run install.packages("remotes")",
            "first in the Console.')
    )
  }
}
if (!require(thesisdown)) {
  if (params$`Install needed packages for {thesisdown}`) {
    remotes::install_github("ismayc/thesisdown")
  } else {
    stop(
      paste(
        "You need to run",
        'remotes::install_github("ismayc/thesisdown")',
        "first in the Console."
      )
    )
  }
}
library(thesisdown)
# Set how wide the R output will go
options(width = 70)
```

```{=html}
<!--
The acknowledgments, preface, dedication, and abstract are added into the PDF
version automatically by inputting them in the YAML at the top of this file.
Alternatively, you can put that content in files like 00--prelim.Rmd and
00-abstract.Rmd like done below.
-->
```
```{r eval=!knitr::is_latex_output(), child=here::here("prelims", "00--prelim.Rmd")}

```

```{r eval=!knitr::is_latex_output(), child=here::here("prelims", "00-abstract.Rmd")}

```

```{=html}
<!-- The {.unnumbered} option here means that the introduction will be 
"Chapter 0." You can also use {-} for no numbers on chapters.
-->
```
# Summary {.unnumbered}

This thesis consists of three chapters. Chapter-[1](#ch1) titled "GDP Measurement in India and the World" provides a broad overview of the history of national accounting. I begin by describing the origins of GDP as a key macroeconomic statistic and a proxy of welfare, tracing its evolution from its conception in the early 17th century, to its standardization and universal recognition in the 20th century. I then briefly describe the various methods of GDP accounting, before delving into the debate on measurement issues in Indian GDP. I conclude by summarizing the debate and stressing on the need for alternative methods to estimate the accuracy of national income statistics in India.
\linebreak

Chapter-[2](#ch2), titled "The Synthetic Control Method" explores the synthetic control method (SCM). I begin by providing a brief introduction to the method, followed by a technical overview of the SCM. I then comment on the various advantages and disadvantages of the SCM, and review the alternative methods which have emerged in recent times to address its lacunae. I then describe the generalized synthetic control method (GSCM), a flexible and widely used alternative to the SCM, and conclude by listing the salient differences between the two. \linebreak

Chapter-[3](#ch3), titled "Estimating measurement error in India's GDP using SCM" uses the SCM and GSCM to construct a counterfactual GDP series, using data from 19 donor countries. I begin by reviewing the literature on GDP measurement error, and synthetic control in macroeconomics, and its usage in the South Asian context. I then specify the identification strategy, describe the data sources, and present the results. Finally, I do a number of robustness checks, and end with a discussion of the results and avenues for future research.
