---
title: 'My Final College Paper'
author: 'Your R. Name'
date: 'May 20xx'
institution: 'Reed College'
division: 'Mathematics and Natural Sciences'
advisor: 'Advisor F. Name'
# If you have more two advisors, un-silence line 7
#altadvisor: 'Your Other Advisor'
department: 'Mathematics'
degree: 'Bachelor of Arts'
knit: bookdown::render_book
site: bookdown::bookdown_site

# The next two lines allow you to change the spacing in your thesis. You can 
# switch out \onehalfspacing with \singlespacing or \doublespacing, if desired.
header-includes:
    - \usepackage{setspace}\onehalfspacing
    - \usepackage{amsmath}
    - \usepackage{amssymb} 

# This will automatically install the {remotes} package and {thesisdown}
# Change this to FALSE if you'd like to install them manually on your own.
params:
  'Install needed packages for {thesisdown}': True
  
# Remove the hashtag to specify which version of output you would like.
# Can only choose one at a time.
output:
  thesisdown::thesis_pdf: default
#  thesisdown::thesis_gitbook: default         
#  thesisdown::thesis_word: default
#  thesisdown::thesis_epub: default

# If you are creating a PDF you'll need to write your preliminary content 
# (e.g., abstract, acknowledgements) below or use code similar to line 25-26 
# for the .RMD files. If you are NOT producing a PDF, delete or silence
# lines 25-39 in this YAML header.
abstract: '`r if(knitr:::is_latex_output()) paste(readLines(here::here("prelims", "00-abstract.Rmd")), collapse = "\n  ")`'
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab 
# is needed on the line after the `|`.
acknowledgements: |
  I want to thank a few people.
dedication: |
  You can have a dedication here if you wish. 
preface: |
  This is an example of a thesis setup to use the reed thesis document class 
  (for LaTeX) and the R bookdown package, in general.
  
# Specify the location of the bibliography below
bibliography: bib/thesis.bib
# Download your specific csl file and refer to it in the line below.
csl: csl/apa.csl
### link highlighting ###
colored-not-bordered-links: true # true = highlight links by coloring text; false = highlight links with a border

# Set the link text/border coloring here, in RGB. 
# Comment out a variable to use whatever the text's existing color is.
# If printing a physical version of your thesis, you'll want to comment out all of these.
urlcolor-rgb: "0,0,139"     # web addresses
citecolor-rgb: "0,33,71"    # citations
linkcolor-rgb: "0,0,139"    # links to sections in your thesis

# Make page number, not text, be link in TOC, LOF, and LOT. Otherwise, section link
# highlighting may look a bit excessive.
toc-link-page-numbers: true
link-citations: yes
linkcolor: blue
always_allow_html: yes
fontsize: 12pt
lot: true
lof: true
---

<!--
Above is the YAML (YAML Ain't Markup Language) header that includes a lot of 
metadata used to produce the document.  Be careful with spacing in this header!

If you'd prefer to not include a Dedication, for example, simply delete the section entirely, or silence them (add # before each line). 

If you have other LaTeX packages you would like to include, delete the # before header-includes and list the packages after hyphens on new lines.

If you'd like to include a comment that won't be produced in your resulting file enclose it in a block like this.

If you receive a duplicate label error after knitting, make sure to delete the index.Rmd file and then knit again.
-->

```{r include_packages, include=FALSE}
# This chunk ensures that the thesisdown package is
# installed and loaded. This thesisdown package includes
# the template files for the thesis.
if (!require(remotes)) {
  if (params$`Install needed packages for {thesisdown}`) {
    install.packages("remotes", repos = "https://cran.rstudio.com")
  } else {
    stop(
      paste('You need to run install.packages("remotes")",
            "first in the Console.')
    )
  }
}
if (!require(thesisdown)) {
  if (params$`Install needed packages for {thesisdown}`) {
    remotes::install_github("ismayc/thesisdown")
  } else {
    stop(
      paste(
        "You need to run",
        'remotes::install_github("ismayc/thesisdown")',
        "first in the Console."
      )
    )
  }
}
library(thesisdown)
# Set how wide the R output will go
options(width = 70)
```

<!--
The acknowledgments, preface, dedication, and abstract are added into the PDF
version automatically by inputting them in the YAML at the top of this file.
Alternatively, you can put that content in files like 00--prelim.Rmd and
00-abstract.Rmd like done below.
-->



```{r eval=!knitr::is_latex_output(), child=here::here("prelims", "00--prelim.Rmd")}

```

```{r eval=!knitr::is_latex_output(), child=here::here("prelims", "00-abstract.Rmd")}

```

<!-- The {.unnumbered} option here means that the introduction will be 
"Chapter 0." You can also use {-} for no numbers on chapters.
-->

# Summary {.unnumbered}

This thesis consists of three chapters. The first chapter titled " GDP Measurement in India and the World" provides a broad overview of the historical evolution of GDP measurement. I first describe the origins of GDP as a key macroeconomic statistic and a proxy of welfare, tracing its evolution from its conception by William Petty in the early 17th century, to the globally accepted and harmonized definition as set out by the United Nations. I then provide a brief history of national acconting in India, before turning my focus to the three methods of output measurement. I then delve into the debate on measurement issues in Indian GDP, focussing on issues emerging in real GDP measurement post 2011.
\linebreak

The second chapter, titled "The Synthetic Control Method" takes a deep dive into the synthetic control method (SCM), which I use to estimate measurement error in Indian GDP in the next chapter. I begin by providing a brief introduction to the method, followed by a technical overview of the SCM. I then comment on the various advantages and disadvantages of the SCM, and review the alternative methods which have emerged in recent times to address the lacunae of the SCM. I then delve deeper into the generalized SCM, a flexible and widely used alternative to the SCM, and conclude by listing the salient differences between the two.
\linebreak

The final chapter, titled "Estimating measurement error in India's GDP using SCM" uses the SCM and GSCM to construct counterfactual GDP series, using data from 19 donor countries. I begin by reviewing the literature on GDP measurement error, and synthetic control in macroeconomics. I then specify the identification strategy, describe the data sources, and present the results. Finally, I do a number of robustness checks, and end with a discussion of the results and avenues for future research.

